### 2017-11-21 manuscript.rmd
spaced out text under simmap plots

#####SIMMAP Sex distribution
```{r sex, echo=F, message=F, warning=F}
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)
```
Posterior probabilities of states (0 Dioecious, 1 Monoecious).

#####SIMMAP Presence of palpons
```{r palpons, echo=F, message=F, warning=F}
#Simmap PALPONS
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```
Posterior probabilities of states (1 Present, 0 Absent).

#####SIMMAP Presence of tentilla
```{r tentilla, echo=F, message=F,warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```
Posterior probabilities of states (1 Present, 0 Absent).

@@

#####SIMMAP Presence of tentilla - *Physalia* corrected
```{r tentilla2, echo=F, message=F, warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim2)
```
Posterior probabilities of states (1 Present, 0 Absent).

@@

#####SIMMAP Nectophore number and types
```{r nectophore_number_types, echo=F, message=F, warning=F}
#Simmap NECTOPHORE TYPES
plotTree(ultratree, lwd = 4)
colors = c("black", "red", "green", "blue")
names(colors) = c("Multiple of one type", "None", "Two of one type", "Two of two types")
necto_types_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(necto_types_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```
Posterior probabilities of states (1 Present, 0 Absent).It is not clear whether or not the stem group of siphonophores had a pneumatophore.

>>>>

#####SIMMAP Sex distribution
```{r sex, echo=F, message=F, warning=F}
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)
```

Posterior probabilities of states (0 Dioecious, 1 Monoecious).

#####SIMMAP Presence of palpons
```{r palpons, echo=F, message=F, warning=F}
#Simmap PALPONS
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

Posterior probabilities of states (1 Present, 0 Absent).

#####SIMMAP Presence of tentilla
```{r tentilla, echo=F, message=F,warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```

Posterior probabilities of states (1 Present, 0 Absent).

@@

#####SIMMAP Presence of tentilla - *Physalia* corrected
```{r tentilla2, echo=F, message=F, warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim2)
```

Posterior probabilities of states (1 Present, 0 Absent).

@@

#####SIMMAP Nectophore number and types
```{r nectophore_number_types, echo=F, message=F, warning=F}
#Simmap NECTOPHORE TYPES
plotTree(ultratree, lwd = 4)
colors = c("black", "red", "green", "blue")
names(colors) = c("Multiple of one type", "None", "Two of one type", "Two of two types")
necto_types_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(necto_types_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

Posterior probabilities of states (1 Present, 0 Absent).It is not clear whether or not the stem group of siphonophores had a pneumatophore.
